Full title of the paper (Capitalized)

### 2023-11-01 Article.Rmd
Commit 2023-11-01 17:09

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Athanasios Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CHP1 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    Mainreferences.bib
linenumbers:     false
numbersections:  true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
output: 
  rticles::mdpi_article: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
# date:           "`r format(Sys.time(), '%F')`"
---

@@

<!-- use SDR for GHI -->

@@

<!-- something about aerosols: bais mail -->
<!-- something about clouds: bais mail -->
<!--
Η εισαγωγή είναι εντάξει. Ίσως θα μπορούσες να βάλεις στη 2η
παράγραφο ακόμη 2-3 σειρές για τις τάσεις του αεροζόλ και των νεφών
από τις εργασίες και να καταλήξεις με κάποια στοιχεία για το αεροζόλ
στη Θεσσαλονίκη από εργασίες δικές μας. Για τα νέφη δεν έχω υπόψη μου
καμία εργασία αλλά ίσως θα μπορούσε να ειπωθεί κάτι χρησιμοποιώντας
παγκόσμιες εκτιμήσεις για την περιοχή της Μεσογείου.
π.χ. https://link.springer.com/article/10.1007/s00382-022-06438-3
-->

@@

...... cloud formation occurrences and constitution nuclei. cite .....
p>        "  Too hard to vim

>>>>

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Athanasios Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CHP1 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    Mainreferences.bib
linenumbers:     false
numbersections:  true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
output: 
  rticles::mdpi_article: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
---

@@

@@

<!--
Η εισαγωγή είναι εντάξει. Ίσως θα μπορούσες να βάλεις στη 2η
παράγραφο ακόμη 2-3 σειρές για τις τάσεις του αεροζόλ και των νεφών
από τις εργασίες και να καταλήξεις με κάποια στοιχεία για το αεροζόλ
στη Θεσσαλονίκη από εργασίες δικές μας. Για τα νέφη δεν έχω υπόψη μου
καμία εργασία αλλά ίσως θα μπορούσε να ειπωθεί κάτι χρησιμοποιώντας
παγκόσμιες εκτιμήσεις για την περιοχή της Μεσογείου.
π.χ. https://link.springer.com/article/10.1007/s00382-022-06438-3
-->

@@

...... cloud formation occurrences and constitution nuclei. cite .....

### 2023-11-01 MDPI_submition.Rmd
Commit 2023-11-01 17:09

    affil: 1,2,* # \ddagger

@@

    affil: 2, \dagger, # \ddagger

@@

      Laboratory of Atmospheric Physics

@@

    email: abais@auth.gr

@@

firstnote: |
  Current address: Updated affiliation

@@

  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.

@@

journal: notspecified

@@

  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.

@@

  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 

@@

informedconsent: |
  Any research article describing a study involving humans should contain this 
  statement. Please add ``Informed consent was obtained from all subjects 
  involved in the study.'' OR ``Patient consent was waived due to REASON 
  (please provide a detailed justification).'' OR ``Not applicable'' for 
  studies not involving humans. You might also choose to exclude this statement 
  if the study did not involve humans.

  Written informed consent for publication must be obtained from participating 
  patients who can be identified (including by the patients themselves). Please 
  state ``Written informed consent has been obtained from the patient(s) to 
  publish this paper'' if applicable.
dataavailability: |
  We encourage all authors of articles published in MDPI journals to share 
  their research data. In this section, please provide details regarding where 
  data supporting reported results can be found, including links to publicly 
  archived datasets analyzed or generated during the study. Where no new data 
  were created, or where data is unavailable due to privacy or ethical 
  re-strictions, a statement is still required. Suggested Data Availability 
  Statements are available in section “MDPI Research Data Policies” at 
  \url{https://www.mdpi.com/ethics}.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
supplementary: |
 The following supporting information can be downloaded at:  
 \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
bibliography: mybibfile.bib
appendix: appendix.tex
endnotes: false
output: 
  rticles::mdpi_article:
    extra_dependencies: longtable
---

@@

The YAML header includes information needed mainly for formatting the front and 
back matter of the article. Required elements include:

```yaml
title: Title of the paper
author:
  - name: first and last name
    affil: |
      One or more comma seperated numbers corresponding to affilitation
      and one or more  comma seperated symbols corresponding 
      optional notes.
    orcid: optional orcid number
affiliation:  
  - num: 1,..., n for each affiliation
    address: required
    email: required
authorcitation: |
  Lastname, F.
correspondence: |
  email@email.com; Tel.: +XX-000-00-0000.
journal: notspecified
type: article
status: submit
```

Journal options are in Table \ref{tab:mdpinames}. The `status` variable should 
generally not be changed by authors. The `type` variable describes 
the type of of submission and defaults to `article` but can be replaced with any of the ones in Table \ref{tab:mdpitype}

```{r mdpitype, echo = FALSE}
type <- c("abstract, addendum, article, book, bookreview, briefreport, 
casereport, comment, commentary, communication, conferenceproceedings, 
correction, conferencereport, entry, expressionofconcern, extendedabstract, 
datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, 
obituary, opinion, projectreport, reply, retraction, review, perspective, 
protocol, shortnote, studyprotocol, systematicreview, supfile, 
technicalnote, viewpoint, guidelines, registeredreport, tutorial")
knitr::kable(rticles::string_to_table(type, 3), 
             col.names = NULL, format = "latex", booktab = TRUE, 
             caption = "MDPI article types.")
```

@@

```yaml
# for journal Diversity,
# add the Life Science Identifier using:
lsid: http://zoobank.org/urn:lsid:zoobank.org:act:nnnn

# for journal Applied Sciences
# add featured application
featuredapplication: |
  Authors are encouraged to provide a concise 
  description of the specific application or 
  a potential application of the work. This 
  section is not mandatory.

# for the journal Data
# add dataset doi and license
dataset: https://doi.org/10.1000/182
datasetlicense: CC-BY-4.0

# for the journal Toxins
# add key contributions
keycontributions: |
  The breakthroughs or highlights of the manuscript. 
  Authors can write one or two sentences to describe 
  the most important part of the paper.

# for the journal Encyclopedia
encyclopediadef: |
  For entry manuscripts only: please provide a brief overview
  of the entry title instead of an abstract.
entrylink: The Link to this entry published on the encyclopedia platform.

# for the journal Advances in Respiratory Medicine
# add highlights
addhighlights: |
  This is an obligatory section in “Advances in Respiratory Medicine”, 
  whose goal is to increase the discoverability and readability of the
  article via search engines and other scholars. Highlights should not 
  be a copy of the abstract, but a simple text allowing the reader to 
  quickly and simplified find out what the article is about and what can 
  be cited from it. Each of these parts should be devoted up to 2~bullet 
  points.

```

>>>>

    affil: 1,* # \ddagger

@@

    affil: 2, #\dagger, # \ddagger

@@

      Laboratory of Atmospheric Physics,

@@

#     email: abais@auth.gr

@@

# firstnote: |
#   Current address: Updated affiliation

@@

  natsisphysicist@gmail.com;
#   Tel.: +XX-000-00-0000.

@@

journal: applsci

@@

  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CHP1 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.

@@

  GHI; SDR; Solar Brigthening/Dimming (list three to ten pertinent keywords specific 

@@

# informedconsent: |
#   Any research article describing a study involving humans should contain this 
#   statement. Please add ``Informed consent was obtained from all subjects 
#   involved in the study.'' OR ``Patient consent was waived due to REASON 
#   (please provide a detailed justification).'' OR ``Not applicable'' for 
#   studies not involving humans. You might also choose to exclude this statement 
#   if the study did not involve humans.
#   
#   Written informed consent for publication must be obtained from participating 
#   patients who can be identified (including by the patients themselves). Please 
#   state ``Written informed consent has been obtained from the patient(s) to 
#   publish this paper'' if applicable.
dataavailability: |
  We encourage all authors of articles published in MDPI journals to share 
  their research data. In this section, please provide details regarding where 
  data supporting reported results can be found, including links to publicly 
  archived datasets analyzed or generated during the study. Where no new data 
  were created, or where data is unavailable due to privacy or ethical 
  re-strictions, a statement is still required. Suggested Data Availability 
  Statements are available in section “MDPI Research Data Policies” at 
  \url{https://www.mdpi.com/ethics}.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
supplementary: |
 The following supporting information can be downloaded at:  
 \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: SDR 
    long: Solar downward radiation
bibliography: mybibfile.bib
appendix:     appendix.tex
endnotes:     false
output: 
  rticles::mdpi_article:
    extra_dependencies:  longtable
    keep_tex:            yes

@@

@@

### 2023-11-01 MDPI_submition.tex
Commit 2023-11-01 17:09

\documentclass[notspecified,article,submit,moreauthors,pdftex]{Definitions/mdpi}

@@

% Authors, for the paper (add full first names)
\Author{Athanasios
Natsis$^{1,2,\ddagger,*}$\href{https://orcid.org/0000-0002-5199-4119}
{\orcidicon}, Alkiviadis Bais$^{2, \dagger,}$}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Aristotle University of Thessaloniki - Laboratory of
Atmospheric Physics Campus Box 149, 54124 Thessaloniki,
Greece; \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}\\
$^{2}$ \quad Your department Street, City,
Country; \href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}\\
}

% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}};
Tel.: +XX-000-00-0000.}

% Current address and/or shared authorship
\firstnote{Current address: Updated affiliation}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
keywords specific to the article, yet reasonably common within the
subject discipline.).}

@@

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

@@

The YAML header includes information needed mainly for formatting the
front and back matter of the article. Required elements include:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{title}\KeywordTok{:}\AttributeTok{ Title of the paper}
\FunctionTok{author}\KeywordTok{:}
\AttributeTok{  }\KeywordTok{{-}}\AttributeTok{ }\FunctionTok{name}\KeywordTok{:}\AttributeTok{ first and last name}
\FunctionTok{    affil}\KeywordTok{: }\CharTok{|}
\NormalTok{      One or more comma seperated numbers corresponding to affilitation}
\NormalTok{      and one or more  comma seperated symbols corresponding }
\NormalTok{      optional notes.}
\AttributeTok{    }\FunctionTok{orcid}\KeywordTok{:}\AttributeTok{ optional orcid number}
\FunctionTok{affiliation}\KeywordTok{:}\AttributeTok{  }
\AttributeTok{  }\KeywordTok{{-}}\AttributeTok{ }\FunctionTok{num}\KeywordTok{:}\AttributeTok{ 1,..., n for each affiliation}
\AttributeTok{    }\FunctionTok{address}\KeywordTok{:}\AttributeTok{ required}
\AttributeTok{    }\FunctionTok{email}\KeywordTok{:}\AttributeTok{ required}
\FunctionTok{authorcitation}\KeywordTok{: }\CharTok{|}
\NormalTok{  Lastname, F.}
\FunctionTok{correspondence}\KeywordTok{: }\CharTok{|}
\NormalTok{  email@email.com; Tel.: +XX{-}000{-}00{-}0000.}
\FunctionTok{journal}\KeywordTok{:}\AttributeTok{ notspecified}
\FunctionTok{type}\KeywordTok{:}\AttributeTok{ article}
\FunctionTok{status}\KeywordTok{:}\AttributeTok{ submit}
\end{Highlighting}
\end{Shaded}

Journal options are in Table \ref{tab:mdpinames}. The \texttt{status}
variable should generally not be changed by authors. The \texttt{type}
variable describes the type of of submission and defaults to
\texttt{article} but can be replaced with any of the ones in Table
\ref{tab:mdpitype}

\begin{table}

\caption{\label{tab:mdpitype}MDPI article types.}
\centering
\begin{tabular}[t]{lll}
\toprule
abstract & entry & retraction\\
addendum & expressionofconcern & review\\
article & extendedabstract & perspective\\
book & datadescriptor & protocol\\
bookreview & editorial & shortnote\\
\addlinespace
briefreport & essay & studyprotocol\\
casereport & erratum & systematicreview\\
comment & hypothesis & supfile\\
commentary & interestingimage & technicalnote\\
communication & obituary & viewpoint\\
\addlinespace
conferenceproceedings & opinion & guidelines\\
correction & projectreport & registeredreport\\
conferencereport & reply & tutorial\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# for journal Diversity,}
\CommentTok{\# add the Life Science Identifier using:}
\FunctionTok{lsid}\KeywordTok{:}\AttributeTok{ http://zoobank.org/urn:lsid:zoobank.org:act:nnnn}

\CommentTok{\# for journal Applied Sciences}
\CommentTok{\# add featured application}
\FunctionTok{featuredapplication}\KeywordTok{: }\CharTok{|}
\NormalTok{  Authors are encouraged to provide a concise }
\NormalTok{  description of the specific application or }
\NormalTok{  a potential application of the work. This }
\NormalTok{  section is not mandatory.}

\CommentTok{\# for the journal Data}
\CommentTok{\# add dataset doi and license}
\FunctionTok{dataset}\KeywordTok{:}\AttributeTok{ https://doi.org/10.1000/182}
\FunctionTok{datasetlicense}\KeywordTok{:}\AttributeTok{ CC{-}BY{-}4.0}

\CommentTok{\# for the journal Toxins}
\CommentTok{\# add key contributions}
\FunctionTok{keycontributions}\KeywordTok{: }\CharTok{|}
\NormalTok{  The breakthroughs or highlights of the manuscript. }
\NormalTok{  Authors can write one or two sentences to describe }
\NormalTok{  the most important part of the paper.}

\CommentTok{\# for the journal Encyclopedia}
\FunctionTok{encyclopediadef}\KeywordTok{: }\CharTok{|}
\NormalTok{  For entry manuscripts only: please provide a brief overview}
\NormalTok{  of the entry title instead of an abstract.}
\FunctionTok{entrylink}\KeywordTok{:}\AttributeTok{ The Link to this entry published on the encyclopedia platform.}

\CommentTok{\# for the journal Advances in Respiratory Medicine}
\CommentTok{\# add highlights}
\FunctionTok{addhighlights}\KeywordTok{: }\CharTok{|}
\NormalTok{  This is an obligatory section in “Advances in Respiratory Medicine”, }
\NormalTok{  whose goal is to increase the discoverability and readability of the}
\NormalTok{  article via search engines and other scholars. Highlights should not }
\NormalTok{  be a copy of the abstract, but a simple text allowing the reader to }
\NormalTok{  quickly and simplified find out what the article is about and what can }
\NormalTok{  be cited from it. Each of these parts should be devoted up to 2\textasciitilde{}bullet }
\NormalTok{  points.}
\end{Highlighting}
\end{Shaded}

@@

\informedconsent{Any research article describing a study involving
humans should contain this statement. Please add
\texttt{Informed\ consent\ was\ obtained\ from\ all\ subjects\ \ involved\ in\ the\ study.\textquotesingle{}\textquotesingle{}\ OR}Patient
consent was waived due to REASON (please provide a detailed
justification).'\,' OR ``Not applicable'\,' for studies not involving
humans. You might also choose to exclude this statement if the study did
not involve humans.

Written informed consent for publication must be obtained from
participating patients who can be identified (including by the patients
themselves). Please state ``Written informed consent has been obtained
from the patient(s) to publish this paper'\,' if applicable.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\sampleavailability{Samples of the compounds \ldots\ldots{} are
available from the authors.}

@@

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}

>>>>

\documentclass[applsci,article,submit,moreauthors,pdftex]{Definitions/mdpi}

@@

% Authors, for the paper (add full first names)
\Author{Athanasios
Natsis$^{1,*}$\href{https://orcid.org/0000-0002-5199-4119}
{\orcidicon}, Alkiviadis Bais$^{2,}$}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Aristotle University of Thessaloniki - Laboratory of
Atmospheric Physics, Campus Box 149, 54124 Thessaloniki,
Greece; \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}\\
$^{2}$ \quad Your department Street, City, Country; \\
}

% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}};}

% Current address and/or shared authorship

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The shortwave downward solar irradiance (SDR) is an important
factor that drives climate processes, production and can affect all
living organisms. While monitoring the long term variability, there are
observations of upward and downward SDR trends on different locations
around the world for different time periods. Periods of positive tredns
are refered as brightening periods and with negative tredns as dimming
periods. We studied 29 years of CHP1 data from Thessaloniki, Greece,
under three sky conditions (clear sky, cloudy sky and all sky
conditions), applying a cloud sky identification algorithm. We found a
positive trend for all-sky and clear-sky conditions, and also,
investigated the consistency of those trends, the effect of the solar
zenith angle, and the variation of the trends for the seasons of the
year. We indentified that there are some anomalies in the long term SDR
trends, for all sky conditions.}

% Keywords
\keyword{GHI; SDR; Solar Brigthening/Dimming (list three to ten
pertinent keywords specific to the article, yet reasonably common within
the subject discipline.).}

@@

@@

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional

@@

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
SDR & Solar downward radiation \\
\end{tabular}}
